---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```


## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```



Test to use a small R Shiny app to demonstrate this function.

```{r, context="setup", include=FALSE}
# load libraries
# library(learnr)
library(shiny)
library(podr)
# set options/configuration
knitr::opts_chunk$set(echo = FALSE)

# load data
cc  <- getOption("podr_tables")
tbs <- as.list(sort(cc$table_name))
```

```{r, context="render", echo=FALSE}
  uiOutput("tabTable")
  DT::dataTableOutput("DT3")
```

```{r, context="server"}
output$DT3 <- renderDataTable({
    tb <- input$tab;
    rr <- data.frame()
    if (is_empty(tb)) { return(datatable(rr)) }
    rr <- get_table_defs(tb) 
    datatable(rr)
  })
output$tabTable <- renderUI({
  cc  <- getOption("podr_tables")
  tbs <- as.list(sort(cc$table_name))
  selectInput("tab", "Table Name: ", multiple = FALSE, choices = tbs  , selected = input$tab)
})
```



```{r}
library(shiny)
library(DT)
library(shinyjs)
library(shinyBS)
library(shinydashboard)

ui <- fluidPage(
  mainPanel(
    tabPanel("Table", uiOutput("tabTable"))
  )
)
server <- function(input, output, session) {
   get_tab_list <- reactive({
    cc <- getOption("podr_tables")
    as.list(sort(cc$table_name))
  })
   
 get_title <- reactive ({
    paste("Table Definition for", toupper(input$tab), sep = " ")
  })

  output$DT3 <- renderDataTable({
    tb <- input$tab;
    rr <- data.frame()
    if (is_empty(tb)) { return(datatable(rr)) }
    rr <- get_table_defs(tb) 
    datatable(rr)
  })
  
  output$tabTable <- renderUI({
    cc <- getOption("podr_tables")
    libs <- as.list(unique(sort(cc$libname)))
    tabPanel("Show"
             , div(id = "form"
                   , selectInput("tab", "Table Name: ", multiple = FALSE
                                 , choices = get_tab_list()  , selected = input$tab)
             )
             , hr()
             , h1(get_title())
             , DT::dataTableOutput("DT3")
    )
  })
}
  shinyApp(ui, server)
```
